---
title: "ds assessment question"
format: html
editor: visual
---

## Packages

```{r}
library(tidyverse)
library(colorblindr)
library(ggmosaic)
library(patchwork)
```


## Disease Screening {#sec-disease-screening}

Medical screening tests are not 100% accurate. It's possible to have a disease but not test positive or not have a disease but test positive for it. The following three visualizations display the outcomes of a medical screening test with a sensitivity (true positive rate) of 98.1% and specificity (true negative rate) of 99.6% in a population where 5% of the individuals have COVID.

We are also interested in the false positive (individuals classified as with a disease, who don't actually have it) and false negative (individuals classified as without a disease, but who do actually have it) rates.

```{r}
#| fig-asp: 0.3
# https://www.fda.gov/medical-devices/coronavirus-disease-2019-covid-19-emergency-use-authorizations-medical-devices/eua-authorized-serology-test-performance
# IgG 	Sensitivity (PPA) 	98.1% (51/52) 	(89.9%; 99.7%)
# IgG 	Specificity (NPA) 	99.6% (2000/2008) 	(99.2%; 99.8%)

sensitivity <- 0.782 #was .981 
specificity <- 0.796 #was .996
n_disease <- 4000 #was 1000
n_no_disease <- 15000 #was 19000
n_disease_positive <- n_disease * sensitivity
n_disease_negative <- n_disease - n_disease_positive
n_no_disease_negative <- n_no_disease * specificity
n_no_disease_positive <- n_no_disease - n_no_disease_negative


disease_status <- c(rep("Disease", n_disease), rep("No disease", n_no_disease))
test_outcome <- c(
  rep("Positive", n_disease_positive), rep("Negative", n_disease_negative),
  rep("Positive", n_no_disease_positive), rep("Negative", n_no_disease_negative)
)
population <- tibble(disease_status = disease_status, test_outcome = test_outcome)

p1 <- ggplot(population, aes(x = disease_status, fill = test_outcome)) +
  geom_bar(colour = "black" , lwd = 1) +
  scale_fill_OkabeIto() +
  theme_minimal() +
  labs(x = "Truth", y = "Count", fill = "Test\noutcome")

p1

p2 <- ggplot(population, aes(x = disease_status, fill = test_outcome)) +
  geom_bar(position = "fill", color = "black", lwd = 1) +
  scale_fill_OkabeIto() +
  theme_minimal() +
  labs(x = "Truth", y = "Proportion", fill = "Test\noutcome")

p2

p3 <- ggplot(data = population) +
  geom_mosaic( offset = 0.02,
              color = "black" , lwd = 1,
    aes(x = product(disease_status), fill = test_outcome),
    show.legend = FALSE
  ) +
  theme_mosaic() +
  scale_fill_OkabeIto() +
  labs(x = "Truth", y = "Test outcome")

p3

(p1 + p2 / p3) +
  plot_layout(guides = "collect") +
  plot_annotation(tag_levels = "A")
```

Fill in the following table by placing a check mark in the cells corresponding to the attributes of the data that can be determined by examining each of the plots.

::: {.content-visible when-format="pdf"}

+-----------------------+------------+------------+------------+
|                       | Plot A     | Plot B     | Plot C     |
+=======================+============+============+============+
| Sensitivity           | [ ]        | [ ]        | [ ]        |
+-----------------------+------------+------------+------------+
| Specificity           | [ ]        | [ ]        | [ ]        |
+-----------------------+------------+------------+------------+
| False positive rate   | [ ]        | [ ]        | [ ]        |
+-----------------------+------------+------------+------------+
| False negative rate   | [ ]        | [ ]        | [ ]        |
+-----------------------+------------+------------+------------+

:::

::: {.content-visible when-format="html"}

+-----------------------+------------+------------+------------+
|                       | Plot A     | Plot B     | Plot C     |
+=======================+============+============+============+
| Sensitivity           | &#9744;    | &#9744;    | &#9744;    |
+-----------------------+------------+------------+------------+
| Specificity           | &#9744;    | &#9744;    | &#9744;    |
+-----------------------+------------+------------+------------+
| False positive rate   | &#9744;    | &#9744;    | &#9744;    |
+-----------------------+------------+------------+------------+
| False negative rate   | &#9744;    | &#9744;    | &#9744;    |
+-----------------------+------------+------------+------------+

:::